CorReg pretreatment : Regression for correlated variables and application in steel industry

### 2014-03-14 www/article13.tex
update
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/correg@449 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

With no constraints on $\hat{p}_1$ when $n<p$ we can have a perfect overlearning, so it is recommended to constrain each $\hat{p}_1^j <n$. Table \ref{compZvraip1max5} shows the impact on the research of such a constraint.

For  \ref{compZnonlin} we have generated non linear structures. Variables in $X_2$ depends on the $\log$ or the square (randomly choosen with equiprobability) of a variable in $X_1$ . Dependencies are still real but non linear.
\begin{table}[h!]
\centering
\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|}
\hline
$n$ & $p_2$ &  $BIC(S)$ & $BIC(\emptyset)$ &$BIC(\hat{S})$  & $TL$ & $WL$ & $ML$ & $\Delta p_2$ & $\Delta compl$ \\
\hline
30 & 16 & ? & ? & ?  & ?  &?  & ?  & ? & ? \\
& &(?) & (?) & (?) & (?) & (?) & (?) & (?) & (?) \\
\hline
\end{tabular} 
\caption{Results of the Markov chain for non linear structure ($\log$ and square). Mean observed and standard deviation (sd). } \label{compZnonlin}
\end{table}

@@

	\subsection{$Y$ depends on all variables in $X$}	 \label{tableMSEsimtout}	
We first try the method with a response depending on all covariates (\textsc{CorReg} reduces the dimension and can't give the true model if there is a structure). The datasets used here were those from \ref{compZvrai}.

@@

& & & cpl (sd) & 17.84 (5.5) & 17.63 (5.6) & 17.84 (5.5) \\ \\

@@

30 & 0 & U&MSE (sd) & 1326.54 (388.4) & 1356.98 (331.4) & 1326.54 (388.4) \\

@@

30 & 16 & U&MSE (sd) & 1400.56 (1598.2) & 668.57 (274.6) & 653.59 (283.7) \\

@@

 &  &HU &MSE (sd) & 1400.56 (1598.2) & 643.25 (277.9) & 653.59 (283.7) \\

@@

\caption{Elasticnet (with Elasticnet) combined with constrained \textsc{CorReg}.$Y$  depends on all variables in $X$. \textsc{CorReg} logically wins}\label{YXlinenet}

@@

30 & 0 & U& MSE (sd) & 1919.43 (861.8) & 2014.13 (683.6) & 1919.43 (861.8) \\

@@

 &  &HU &MSE (sd) & 1919.43 (861.8) & 1885.39 (814) & 1919.43 (861.8) \\

@@

\clearpage
	\subsection{$Y$ depends only on covariates in $X_2$ (worst case for us)}	 \label{tableMSEsimgauche}
We now try the method with a response depending only on variables in $X_2$. The datasets used here were still those from \ref{compZvrai}.
Depending only on $X_2$ imply sparsity and impossibility to obtain the true model when using the true structure.

@@

	\clearpage	
\section{Numerical results on real datasets}
\subsection{Quality case study}
This work takes place in steel industry context, with quality oriented objective : to understand and prevent quality problems on finished product, knowing the whole process.

>>>>

@@

	\subsection{$Y$ depends on all variables in $X$}	 \label{tableMSEsimtout}	
We first try the method with a response depending on all covariates (\textsc{CorReg} reduces the dimension and can't give the true model if there is a structure). The datasets used here were those from \ref{compZvrai}.

We observe that \textsc{CorReg} is better than classical methods especially whith the Hierarchical Uniform law. When the complexity of the true model is higher than $\frac{p}{2}$ Uniform hypothesis logically is better but (HU) still beats classical methods. We also observe that simple methods like stepwise (here from the package \textsc{lars}) give good results in prediction.

It is also notable that (HU) has a greater computational cost than (U). But next versions of the package may optimize a bit more the penalization step and reduce this gap.

@@

& & & cpl (sd) & 17.84 (5.5) & 17.63 (5.6) & 17.84 (5.5) \\ 

@@

30 & 0 & U&MSE (sd) & 1 326.54 (388.4) & 1 356.98 (331.4) & 1 326.54 (388.4) \\

@@

30 & 16 & U&MSE (sd) & 1 400.56 (1598.2) & 668.57 (274.6) & 653.59 (283.7) \\

@@

 &  &HU &MSE (sd) & 1 400.56 (1598.2) & 643.25 (277.9) & 653.59 (283.7) \\

@@

\caption{Elasticnet combined with constrained \textsc{CorReg}.$Y$  depends on all variables in $X$. \textsc{CorReg} logically wins}\label{YXlinenet}

@@

30 & 0 & U& MSE (sd) & 1 919.43 (861.8) & 2 014.13 (683.6) & 1 919.43 (861.8) \\

@@

 &  &HU &MSE (sd) & 1 919.43 (861.8) & 1 885.39 (814) & 1 919.43 (861.8) \\

@@

\clearpage
	\subsection{$Y$ depends only on covariates in $X_2$ (worst case for us)}	 \label{tableMSEsimgauche}
We now try the method with a response depending only on variables in $X_2$. The datasets used here were still those from \ref{compZvrai}.
Depending only on $X_2$ imply sparsity and impossibility to obtain the true model when using the true structure. \textsc{CorReg} is still better than classical methods.

@@

\clearpage
\subsection{Non linear case}
 we have generated non linear structures (Tables \ref{compZnonlin} and \ref{resYnonlin}). Variables in $X_2$ depends on the $\log$ or the square (randomly choosen with equiprobability) of a variable in $X_1$ . Dependencies are still real but non linear. \textsc{CorReg} still found dependencies. One example of non-linear structure found with \textsc{CorReg} on real datasets is given in section \ref{sectionexfos}.
\begin{table}[h!]
\centering
\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|}
\hline
$n$ & $p_2$ & $\psi$ &Time Mixmod  & Time MCMC  & $TL$ & $WL$ & $ML$ & $\Delta p_2$ & $\Delta compl$ \\
\hline
30 & 16 & U& 0.4313 & 2.7769 & 9.96 & 2.45 & 5.95 & 3.5 & 29.42  \\
& & &(0.0391) & (0.0883) & (1.3175) & (1.3808) & (1.3056) & (1.453) & (6.2639) \\
 &  & HU & 0.4313 & 4.9079 & 7.28 & 1.25 & 8.63 & 7.38 & 5.77  \\ 
& & &(0.0391) & (0.4353) & (1.5769) & (0.9987) & (1.5548) & (1.6316) & (6.1297) \\ 
\hline
\end{tabular} 
\caption{Results of the Markov chain for non linear structure ($\log$ and square). Mean observed and standard deviation (sd). } \label{compZnonlin}
\end{table}

\begin{table}[h!]
\centering
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline 
$n$ & $p_2$&  $\psi$ &indicator &LASSO  &    \textsc{CorReg} $\hat S$& \textsc{CorReg} $S$\\ 
\hline %nonlin0.5global30p40ratio0.4BICTRUEBICstarTRUEp1max5lambda5100Amaxp2max100sigma_sousreg0.001maxit9000maxtry20max_compl1scaleTRUEcandidates-1_12mars2014_19_55_33.csv
30 & 0 & U&MSE (sd) & 996.06 (323.7) & 1100.17 (391.4) & 1501.25 (905.9) \\
& & &cpl (sd) & 17.66 (5.4) & 14.7 (4.7) & 11.97 (4.9) \\
 &  &HU &MSE (sd) & 996.06 (323.7) & 1094.5 (621.8) & 1501.25 (905.9) \\
& & & cpl (sd) & 17.66 (5.4) & 16.98 (4.8) & 11.97 (4.9) \\ 
\hline
\end{tabular} 
\caption{ $Y$ depends on all variables in $X$. \textsc{CorReg} is not too far from LASSO.} \label{resYnonlin}
\end{table}

	\clearpage	
\section{Numerical results on real datasets}
\subsection{Quality case study} \label{sectionexfos}
This work takes place in steel industry context, with quality oriented objective : to understand and prevent quality problems on finished product, knowing the whole process.
